\documentclass[utf8]{ctexart}
\usepackage{geometry}
\usepackage{ulem}
\geometry{a4paper,scale=0.8}
\author{Mineral}
\title{作文}
\date {\today}
\begin{document}
		\maketitle
		\subsection{替换词}
		\begin{itemize}
				\item change -> transform : It's that event that transform my life significantly.
				\item good -> fabulous, splendid, magnificent [magnifcant 宏大的，雄奇美丽的]	
				\item 	crowded 人,flock 动物
				\item in consideration of = in view of
				\item aiming to = with a view to
				\item atmosphere < mood ： Her mood darkened at the news.
				\item lighten - darken : My sunny mood suddenly darkened.
				\item mount > increase : The pressure for change continued to mount.
				\item general = rough : To understand the rough/general framework of your major.
		\end{itemize}
		\subsection{翻译}
		\begin{itemize}
				\item breathe a sigh of relief
				\item We all heaved a sigh of relief.	

		\end{itemize}
		\subsection{复合词}
		\begin{itemize}
				\item aboveground adj\& adv.地上 : The repository stand aboveground suddenly explode into fragments.
				\item airconditioner n.空调
				\item airfield n.飞机场 airline n.定期航线 airliner n.定期班机，客机 air-mail v.adj.n. 航空邮寄 
				\item airproof a.不通气的，不透气的 v. 使气密
				\item airship n.飞艇飞船
				\item airsick adj.晕机的  airspace n.领空，空域 ： Elsewhere, in uncontrolled airspace, pilots are bound 
						by fewer regulations.  [regulations n.管制]
				\item alongside adv.在旁 : A police car pulled up alongside us.
				\item artwork n.艺术品 masterpiece=masterwork=杰作名著
				\item backstage n.后台 : Her fans crowded backstage, and asked for autograph.
				\item backyard n.后院 bathhouse n.澡堂
				\item 		battlefield n.战场 : Hero earned glory on battlefield but lived a poor life.
				\par I conceal myself at a safe distance from battlefield at length.
		            \item bedtime  : What's worse, it would get children overactive just before bedtime. 	
		            \item beforehand adv.预先 : Every step should be considered detailedly beforehand.
		            \item best-seller n.畅销书 : The book is expected to dominate the best-seller lists.
		            \item birthdate 出生年月日 birthday 生日 birthrate 出生率			
					\item bittersweet adj.苦甜交集的 : Family is filled with overwhelming and bittersweet moments.
					\item perceive v.认为理解 : The discovery is perceived as a significant breakthrough.
					\item breakup n.断开分手 He was down with the breakup of marriage.
					\item bystander n.旁观者  It looks like an innocent bystander was killed instead of you.
					\item bulletproof a.防弹的 n.bullfighter n.斗牛士
					\item burdensome a.成为负担的 Regulations are growing more burdensome.
					\item campout n.野营 candlelight 烛光 :
					\item distinguished guest n.嘉宾
					\item chairman chairwoman 主席\sout{狗}男女 cheerleader 啦啦队长
					\item cornerstone : Research is the cornerstone in academic realm.	
					\item countrywide 全国性的 cowboy 牛仔 cross-section n.横截面	
					\item dawnlight n.晨曦 Dawnlight lightened the end of the tunnel.	
					\item deeply-considered a.深思熟虑的 doorbell 门铃
					\item doorstep 门阶 doorway 门口
					\item foothold n.立足处 footprint n.脚印 footballer n.足球运动员
					\item fingertip n.指尖
					\item second-hand 二手的			
							

	

		\end{itemize}
		\subsection{野句}
		\begin{enumerate}
				\item Luxury and bling is not what we march for.
				\item The animation has obtained the magnificent achievement at first in China, in domestic and 
						foreign is welcomed deeply and has produced profound influence
					\item There is no royal road to learning. [学无坦途]
		\end{enumerate}
		
		
\end{document}
