\documentclass[utf8]{ctexart}
\usepackage{geometry}
\geometry{a4paper,scale=0.8}
\author{Mineral}
\title{听课手册}
\date {\today}
\begin{document}
		\maketitle
		\section{词组}
		\begin{enumerate}
				\item Long before 很久之前: Long before I went to Africa, it was alive in my imagination.
				\item before long 不久以后	
				\item go through and Get through[克服]
					\par I go through my homework to make sure.
					\par I get through everything but English.	
			\item upset
					\par The memory of sorrow upsets me consistently.
					\par He upset my arrangement to travel along the world.	
					 
			\item set aside 拨出时间金钱等，不顾
			\par She set aside her daughter and explore surface of Earth thoroughly.		
				\item thoroughly: He thought it's a thoroughly deserved victory but not the hollow one.
				\item go in for: We all go in for winter sport. [爱好]	
				\item be doomed to: Those who go in for conspiracy are doomed to failure.[注定]
						\par 那我就要注定流浪了: And I'll be doomed to eternal wandering.
			    \item 她性格文静，和蔼可亲: She is quiet and good-natured, so she is the most easiest person in the world to get along with.
			    \item remember of: All I can remember of the previous few days is pieces broken on the dull ground.		
			    \item on a regular basis: The general manager drops into the restaurant on a regular basis so the staff member have to be on their toes any at all the times.
						\par 注意，一个抽象名词的关联介词与其动词形式词组介词紧密相连
				\item On the basis of : Any action based on such fragmentary evidence is silly.
				\item fragement: She read everything, digesting every fragment of news.
                \item at one's command 受某人控制
		        \item make use of to do sth. 
		        \item be made use of to do sth.	
				\item Be pulled down to make room for: 脱下裤子是为了穿上新的[拆毁]	
				\item Play a XXX role = Function as	
				\item Persuade/talk sb out of : I could't persuade him out of resolution.	
				\item Ever since put up the firm armour, I have had to regulate every step cautiously.	
				\item come into view : The scenery gradually came into view as she stepped forward. 	
				\item behind schedule : We seem to have slipped behind schedule.
				\item In case of : She has prepared financially in case of accident.
				\item In view of : In view of his financial conditon, no risky decision should be made <though> with great determination. 		
				\item view as : Newer players are stepping into what they view as a treasure house.
				\item give back : Other than what I've done, I can't give back any more.
				\item give in to : My family insisted that I should't give in, but stay and fight.
				\item insist : 1.坚持主张 2.坚持认为  薛定谔的虚拟语气
				\item insist on : Our customer insisted on high quality.
				\item shock 冲击 打击 ： She was shocked at/by her wallet's disappearance.
				\item put away : can you put away your toys?
				\item stick to : If you want to play an instrument well, you should stick to it.
				\item come down to : Never would I think he has come down to begging.
				\item Deeply burried in thought, She wrinkled her frown sightly.
				\item worth : Such delicious food is worthy of attempt.
				\item flock : Scattered animals abruptly flock to the broken fence.
				\item free of charge = for free	 
				\item charge sb. for sth. : I will charge you for my protection.
				\item pick up : The hospital can't pick up more patients anymore.
				\item pick out : Scarcely had I picked out my wife when I break into the apartment.		
				\item At the mercy of : The little boat is at the mercy of huge storm.
				\par So pitifully did she plead that the Lord grew calm and decide to have mercy on her.
				 \item put the blame on sb. : God never puts blame on people's dullness, but people put blame on god's unjust.
				\par They cried for mercy but their mercy but their pleas met with their laughter and abuse.
				\item succeed 接任 继承 : He succeeded his father as manager of the company.
				\item I heard my truck started thunderously and then fade away.	
				\item tunnel-隧道 channel-管道，频道，海峡	
				\item get down to : Let's get down to some serious work.
				\item On no account = In no case
				\item Seek one's fortune 寻找发迹的机会
				\item Seek out 物色，找到，找出 ： Seek out your friend among
						your classmates! 
				\item undertake 承担,承诺
				\item bring about 引起导致 bring down 几百 bring out 出版，使显现，生产 bring in 赚得，吸引，引入
				\par He shielded his eyes against the dazzling decling sun.		
				\par Rather than just dazzling with high cool factor, there is a focus on the pratical.
				\item pull through 使\ldots 渡过难关，康复 : I relied on my instincts to pull me through.
				\item confirm one in one's belief : Just confirm yourself in your belief.	
				\par the line between good and evil is beginning to blur.	
				 \item General knowledge 常识
				 \item Express delivery 快递
				 \item pay on delivery 到货付款
				 \item vary in : The suggestions put forward on conference vary in importance and influence.
				 \item vary from : The activities vary from appreciate representative masterwork to yoga.
				 \item come to life ： The market gradually came to life as the sun rose.
				 \item model after/on : Our sculpture is modeled after The David.
				 \item attend to 处理，照顾 : I have some urgent business to attend to  			
			     \item attemps : Attempts have been made to find out the causes of the plane crash, but without luck so far.
				\item appeal : They take their appeal to Supereme Court	[起诉]
				\item We tend to have a better memory for things that excite our senses or appeal to our emotions than for straight facts.		
				\item break away from 脱离（政党等），放弃，打破（成规），挣脱 : The thief tried to break away from the policeman, but he failed.
				\item make out : In the dim light, I could just make out a tall, shadowy figure crossing through the undergrowth.
				\item let out a sigh of relief  		
		
			


		\subsection{辅元辅双写例外}
		同时需要满足重音在最后一个
		\begin{itemize}
				\item open
				\item control	
				\item happen
				\item cover
				\item visit
				\item borrow
				\item suffer
				\item travel
				\item cancel			
						
		\end{itemize}
		

		\end{enumerate}
		\section{语法}
		\subsection{限制性与非限制性定语从句}
		\Large 限制性意味着在句子中十分重要珍贵。
		\subsection{先行词被修饰时的限制}
		\begin{itemize}
				\item 被序数词修饰
				\item 被最高级修饰
				\item 被 all, much, many, any 语焉不详者修饰
				\item 先行词为 something, anything, something, everything, nothing 语焉不详者			
		\end{itemize}
		\Large 只能使用that. 个人认为that更能承接气势，所以有强调从句的作用
        \par It is at that night that he told me the truth of the world.
		
		
		
		
\end{document}
