\documentclass[utf8]{ctexart}
\author{Mineral}
\title{English Words}
\date {\today}
\begin{document}
	\maketitle
	\section{Recite}
	\subsection{Note}
	\par the very night $\to $
	\par the very important night	 
	
	\subsection{Words-Day12}
	\par in company 
	\par in concert 	
	\par count 认为
	\par cover v.够付
	\par course n.一道菜
	\par be cross with sb. adj.生气的
	\par cut vt.砍，割
	\par His rude remarks cut me.
	\par causal adj.偶然的，随意的
	\par He was employed as a causal laborer.											
	\par cater v.承办酒席，提供饮食  v.满足需要，迎合
	\par caution v.告诫提醒
	\par chance v.碰巧
	\par She chanced to be in when he called.
	\par charge v.赋予责任或义务
	\par Mother charged Alice to take good care of the baby.
	\par challenge v.挑战
	\par I challenged him to a game of chess.
	\par clean adj.干净的
	\par I clean forgot about it.
	\par He conducted himeself far better than expected. v.举止表现
	\par I congratulated myself (on my escape). v.为成功感到高兴或自豪
	\par The fire soon consumed the old wooden buildings in the neighborhood. vt.烧毁，毁灭
	\par economize on = save sth. instead of being wasteful
	\par be in effect= be in operation					
	\section{Cloze Test}
	\subsection{2012.11绍兴}
	\par custodian n.门卫
	\par squarely adv.直截了当地	
	\par step up to the challenage.	
	\par She squarely shoulder her family respoinsibilities.	
	\par mayor n.市长
	\par This sentiment was echoed by TerranMayor.
	\par curve 弯曲 carve 雕刻
	\par sentiment n.观点
	\par commitment n.承诺保证，投入献身
	\par credit 1.荣誉声望2.信用3.学分4.余额5.补助6.作品
	\par over the course of six months
	\par bias n.偏见	
	
	
	\section{Writting Materials}
	\subsection{The Woodcutter's Wishes}
	\par cottage n.小屋，村舍
	\par dish out 把(菜肴)等装盘端上；(用餐时)分(饭菜)	
	\par porridge n.粥，糊
	\par chill n.寒冷;寒气;寒战		
	\par As Hilda dished out porridge one morning, a chill made her shiver.
	\par chop vt.切细剁碎 -vi.用力切砍
	\par shiver vi.颤抖，哆嗦，帆迎风拍动
	\par ax n.=axe 斧子战斧行刑斧				
	\par enormous a.庞大的，巨大的
	\par trunk n.象鼻,树干，鸟或昆虫的喙		
	\par swing 	vt. 使旋转,挥舞
	\par wee adj.绩效的，很小的，很早的
	\par beg(begged,begging) vt.乞求，请求		
	\par fairy n.小精灵	
	\par startle vt.使吓一跳
	\par This startle the ax and it dropped the woodcutter.	
	\par grant vt.同意准予授予承认	
	\par burst vi.爆裂，突然发生
	\par pant vt.气喘;悸动，剧跳
	\par track vi.留下足迹;运行;走
	\par rip n.裂口，裂缝
	\par mend vi.渐愈;好转 vt.修补缝补
	\par rumble vi.肚子饿发出的咕咕声
	\par At sunset, the woodcutter's stomach began rumbling.
	\par quarrel (quarrel(l)ed)
	\par sausage n.香肠
	\par shriek vt.尖声发出
	\par dangle vi.悬荡
	\par tug（tugged;tugging）用力抓，拖拽
	\par vanish vi.消失突然不见逐渐消散	
	\par at once 马上立刻=instantly
	\par At once, the sausages vanished. And so did the couple's three wishes.	
	\section{Grammar}
	\subsection{Virtual Tense}
	\par Wish 的从句要使用虚拟语气
	\par 1.对现在的虚拟 过去时(be的过去时用were)
	\par 2.对过去的虚拟 had + 过去分词
	\par 3.对将来的虚拟 would/could/might+ 动词原形			
	\par would rather 的\textbf{宾语从句}从句也类似，不过不大一样
	\par 1.对现在的虚拟 \& 对将来的虚拟 过去时(be->were)	
	\par 2.对过去的虚拟 had+ 过去分词	
	\par I would rather he had gone to the seaside with me the day before yesterday.	
	\par  


	
	
	\section{Listensing}
	
	

	
	
\end{document}
